\sysfull

### 2017-11-14 paper/compiler.tex
pass over all but generation

The task boundary identification analysis processes a standard C program (as
shown in Figure~\ref{fig:compiler_overview}) and produces a CFG with some
vertices marked as {\em task boundaries}. The \sys compiler builds the
program's CFG as shown in Figure~\ref{fig:compiler_overview}. In our simple reference prototype, 
we implemented inter-procedural analysis by inlining all functions called.   Recursive function call cannot be handled, so the
programmer has to rewrite it into a non-recursive call if there is one. The
approach of always inlining function calls will introduce code duplication. If
the code size is problematic, alternative approach is to make each function
call a task boundary. We leave implementation of such alternative strategy as a
future work.
%
%\sys uses a cost-based task boundary placement analysis that considers per-block energy consumption estimates, inter-task variable liveness, and the cost of partitioning loops.
%
We first describe how \sys measures each of these costs and then describe
\sys's procedure for placing boundaries in the CFG.

@@

\sys's task cost analysis considers estimated task energy cost, variable liveness, and the impact of splitting loops across tasks. The result of this analysis determines where to place boundaries in the CFG.

{\noindent \bf Estimated energy cost.} \sys assigns each basic block in the CFG a {\em cost}, which is an estimate of the energy consumption of the block. Precisely modelling the energy cost of arbitrary C code is a difficult problem and beyond the scope of this work; we simply use the number of intermediate representation (IR) instructions in a block as a proxy for energy because more instructions mean more energy consumption. Moreover, we assume as an input to the compiler the maximum number of operations that the device can execute without exhausting its buffered energy. This parameter is highly device-dependent, and we assume that a developer or device manufacturer determines the number empirically, as we did in this work through direct measurement. \sys's analysis tries to ensure that the estimated energy cost of different tasks is roughly the same and does not exceed given energy budget (which is part of the boundary placement process described later).

{\noindent \bf Live variable cost.} Each CFG edge is associated with a set of variable that {\em may} be {\em alive} across the edge (i.e., variables whose value may be consumed later on). Variables that live across an edge must be protected by \sys's memory virtualization mechanism when boundary is placed at the edge and the resulting inter-task variable increases the run time overhead. \sys's tries to minimize the overhead of protected variables by placing boundaries to minimize the number of inter-task live variables.

{\noindent \bf Loop cost.} Loops are a challenge for \sys because the analysis must account for the cost of multiple iterations of the loop body. \sys assumes that most loops are
annotated with a static loop bound. For loops that do not have a static bound, \sys conservatively assumes the loop will be too large to fit within a single task.

>>>>

The task boundary identification analysis processes a standard C program (as
shown in Figure~\ref{fig:compiler_overview}) and produces a CFG with some
vertices marked as {\em task boundaries}. The \sys compiler builds the
program's CFG as shown in Figure~\ref{fig:compiler_overview}. In our simple
reference prototype, we implemented inter-procedural analysis by inlining all
functions called.  We opted not to support recursion, which is uncommon in
embedded code. We leave to future work better approaches to interprocedural
analysis and task transformation.

%
%\sys uses a cost-based task boundary placement analysis that considers per-block energy consumption estimates, inter-task variable liveness, and the cost of partitioning loops.
%

@@

\sys's task cost analysis considers estimated run time, the liveness of
variables and the cost of splitting loops across tasks. The result of the task
cost analysis determines where to place boundaries in the CFG.

{\noindent \bf Estimated run time.} \sys assigns each basic block in the CFG a
{\em cost}, which is an estimate of the run time of the block.  Precisely
modeling the run time and energy cost of arbitrary C code is difficult and
beyond the scope of our simple compiler prototype.  Instead, our prototype counts
LLVM intermediate representation (IR) instructions and assigns a higher cost to
a block with more operations, assuming that the block runs for a longer period
of time and consumes more energy.  
%
To make the cost estimate useful, our compiler prototype estimates the maximum
cost that the device's energy buffering capacitor supports.  \sys estimates
this quantity by measuring the number of arithmetic operations that can execute
without a power interruption, starting from a full capacitor. This maximum number
of operations is a limit on the cost of a task -- any longer task risks not
executing to completion.

{\noindent \bf Live variable cost.} Each CFG edge is associated with a set of
variables that {\em may} be {\em alive} across the edge (i.e., variables
assigned before the edge and may be read after the edge). Variables that live
across an edge must be protected by \sys's memory virtualization mechanism when
\sys places a task boundary on the edge.  \sys heuristically minimizes variable
virtualization overhead by placing boundaries to minimize the number of
live variables that span task boundaries.

{\noindent \bf Loop cost.} Loops are a challenge for \sys because the analysis
must account for the cost of multiple iterations of the loop body. \sys assumes
that most loops are annotated with a static loop bound. For loops that do not
have a static bound, \sys conservatively assumes the loop will be too large to
fit within a single task. Assuming loop bounds is a reasonable simplification:
while not always the case, long loops in embedded code are often statically
bounded, especially when code aims to meet strict resource requirements.
